Clines from PDE

### 2015-11-24 notes/pde-clines.Rmd
pde clines
.

xgrid <- setup.grid.1D(x.up=-20, x.down=20, N=10)
rgrid <- setup.grid.1D(x.up=-0.5, x.down=0.5, N=50)

@@

>>>>

xgrid <- setup.grid.1D(x.up=-20, x.down=20, N=10)
rgrid <- setup.grid.1D(x.up=-0.5, x.down=0.5, N=40)

@@

**Note:** do the same with fixed distance between the two and changing distance to selected locus.
